Timely Object Detection

### 2012-03-05 writeups/eccv12/technical.tex
almost done with technical

@@

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf_1.pdf}
\caption{
We present a point in the middle of the decision process for 3 classes; one action has already been taken.
\comment{Some classifiers have already been observed.}
}
\label{fig:model}
\end{figure}

@@

\subsection{Policy parametrization and more reward functions}

@@

\todo{here introduce the view of learning parameters given the observed rewards}

Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total expected reward of a policy $\pi$ is then defined as the sum of rewards
\begin{equation}
\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
\end{equation}

The reward function does not necessarily have to be related to the evaluation of the system.

\subsubsection{Slope of performance vs. time}
\begin{figure}[htb]
  \centering
  \includegraphics[width=0.56\linewidth]{figures/apvst_expl.pdf}
  \caption{A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action. The figure shows this analysis for the action highlighted in orange.}
  \label{fig:rewards}
\end{figure}

Remembering that the final evaluation of a policy consists of the area under the performance vs. time curve, we formulate per-action rewards such that their addition results in precisely this quantity.
Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
\Delta AP (t_T-\Delta t)
\end{equation}
where $t_T$ is the time left until deadline, and $\Delta t$ and $\Delta AP$ are the time taken and AP change produced by the action.

The equation breaks down into a term to maximize, $\Delta AP t_T$, and a term to minimize, $\Delta AP \Delta t$.
This agrees with the intuition that to capture the most area under the curve, the slope needs to be maximized at each point.
Additionally, the equation shows that if $\Delta t$ exceeds $t_T$, the value of taking the action is negative.

At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.

First, we seek to maximize the expected next-stage reward, and manually construct a value function such that picking the action with maximal value achieves this.
Next, we note that the manually constructed value function can be represented as a scalar product of a parameter vector with a featurization of the belief state; we learn the weights by regression to the actual next-stage reward from running many episodes.
Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.

\subsubsection{Learning the weights}
We note that we can represent the one-step greedy policy value function as a scalar product

>>>>

One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.
Of course, we'd like to learn the value function from the data, but the above heuristic will be used as a baseline in the evaluation to follow.

@@

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf_1.pdf}
\caption{
The MRF inference model used in our system.
We show a point in the middle of the decision process for 3 classes; one action has already been taken.
\comment{Some classifiers have already been observed.}
}
\label{fig:model}
\end{figure}

@@

\subsection{Learning the Value Function}

Remember that our heuristic value function consisted of picking the action corresponding to the class presence variable with the highest probability $P(C_k)$.
We can formulate such a policy as a scalar product:
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A}} \theta^\top \phi(b,a_i)
\end{align}
where $\phi(b,a_i)$ is a feature vector representation of the belief state.
This approach is known as function approximation in reinforcement learning \cite{Sutton1998}.

Let us take take the feature representation for an action $a_i$ to be $[P(C_k), \, 1]$, where $C_k$ corresponds to the action.
This corresponds to our heuristic value function, with a bias variable.
The feature representation $\phi(b,a_i)$ then is a vector of size $F|\mathcal{A}|$, with $F=2$ for this feature, where all values are $0$ except those corresponding to $a_i$.

This representation allows us to use a single vector of weights $\theta$ as a compact representation of our policy.

@@

One feature we want the reward function to have is additivity.
Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total reward of a policy $\pi$ starting at state $b^j$ is then defined as the sum of rewards
\begin{equation}
R(h^j) = \sum_{j'=j}^J R(b_j')
\end{equation}

We formulate two reward definitions: one strives to match the final AP evaluation of the detections, and one is motivated by lowering uncertainty of $P(\mathbf{C})$.

\subsubsection{Reward: area under the AP vs. Time curve}
\begin{figure}[htb]
  \centering
  \includegraphics[width=0.56\linewidth]{figures/apvst_expl.pdf}
  \caption{A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action. The figure shows this analysis for the action highlighted in orange.}
  \label{fig:rewards}
\end{figure}

The final evaluation of a policy consists of the area under the performance vs. time curve.
Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.
Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}_i)t_T^j}
\end{equation}
where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.

\subsubsection{Reward: decrease in mean entropy}
We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$.
As with the above policy, the decrease in entropy is considered with regard to the time of the action.

The goal of a policy that maximizes these rewards is to take actions that reduce uncertainty of the most uncertain variables most quickly.

\subsection{Learning the weights}

\todo{Describe the greedy thing and the generalized policy iteration that we do.}
